---
title: "Simple Linear Regression"
output: 
  html_document:
    theme: cerulean
    code_folding: hide
---

```{r message=FALSE, warning=FALSE}
# Load your libraries
library(pander)
library(car)
library(DT)
library(mosaic)
library(tidyverse)

# Load your data after saving a csv file in your Data folder.
# You can use either 
My_data <- read.csv("../../Data/LinearRegression.csv", header=TRUE)
# or
#   library(readr)
#   someName <- read_csv("../Data/YourDataFileName.csv")

# Don't forget to run "Session -> Set Working Directory -> To Source file location"

```


## Background
The following  dataset labelled MY_data is a personal data set that i got from my friends here at BYU Idaho mostly my roomates. I asked them how much they study and their grade for a certain class.



## Introduction

Good Grades are important in school, So how do we get these good grades ?  A good analysis thats seems to be reliable is checking if the amount of effort put into studying has any impact on a persons grade in a particular class. But at the same time they say all work and no play makes Jack a dull boy so maybe over studying may have dminishing returns.




## Hypothesis Test
Null hypothesis says that there is no relationship between study hours and the grade that a person got.

$$
  H_0: \beta_1 = 0
$$



$$
\alpha = 0.05
$$

I am using an alpha level of 0.05






The Ha Hypothesis is saying that X and Y are related so a persons grade is related to the hours they put into their study or their grade is predicated on the amount of time in Hours spent studying.

$$
  H_a: \beta_1 \neq 0
$$





$$
  \text{Grade} = 58.75 + 4.25  \times \text{(Study Time in hours)}
$$

### Explanation of the Equation.
From the above Hypothesis we are assuming that for every additional hour of study, a persons grade will increse by 4.25 points. 








## Regression Model 

```{r warning=FALSE}
regret.lm <- lm(Grade ~ Hours.Studied, data=My_data)
pander(summary(regret.lm))
```








$$
  \underbrace{\hat{Y}_i}_\text{Ave.Grade.} = 58.75 + 4.25 \underbrace{X_i}_\text{Study Time in Hours }
$$








## Graphical Summary
```{r}
plot(Grade ~ Hours.Studied, data=My_data, pch=20, col="firebrick", cex=1.2, las=1,
     xlab="Hours of Study Time Applied ", ylab="Grade attained",
     main="Does More study Time Better my grades or not")

abline(regret.lm, lwd=2, col="pink")
```

## Explanation
The above plot shows the hours of study time applied and the grade that a person gets in a class, from this plot we see that the more hours applied to studying the better the grade.





## Numerical summary.
```{r warning=FALSE}

favstats( My_data$Hours.Studied) |> pander()
```
```{r warning=FALSE}
favstats( My_data$Grade)|>pander()
```

## Explanation 
The above numerical summary has been split into two groups for each numerical variable. The X axis which is the study time has a mean of 6.7 hours and shows a sample size of 9. The Standard Deviation is 3 hours. On the other hand the Grade is the X variable and has a St dev of 13 points, The mean grade is 87.56 points out of 100.



```{r}
par(mfrow=c(1,3))
plot(regret.lm, which=1)
qqPlot(regret.lm$residuals, id=FALSE)
plot(regret.lm$residuals, main="Residuals vs Order")
```

## Assumption Plot Interpretation.
There is a linear relationship problem with the data because the residual vs fitted have a sharp downward curve. On the residual vs order there is a sharp curve too. The Constant variance is not too much of an issue even though there is curvature. The other plot is the normality plot and it looks good because the data points are on the line. The third plot is for independence and there seems to be a problem because the data does not seem independent because theres a pattern.







<!-- Directions


Come up with a simple linear regression of your own creation. 

```


* Write the Background and clearly state your question. Then collect data and perform the linear regression analysis in order to answer your question. Use the proper order of first, ask the question, then second, figure out the answer.

* You should collect both the quantitative response variable and the quantitative explanatory variable yourself. This can be data you collect from 
    - the internet (like weather data, Facebook data, or sports data) 
    - your own experiment 
    - your own observational study
* However,     
    - The data should not be a single pre-existing dataset. It must be something that you piece together yourself.

* You need at least $n=3$ $(X,Y)$ pairs to perform the regression. However, your regression will only be useful if you can get around $n=10$ or more observations.

-->


## Conclusion
The P value  was significant low so the more a person studies, their grade increases as well. But one of the most important assumptions is that there must be a linear relationship between the x and y variables. since this important assumption is not met, then we cant trust the data.



